A multinomial spatio-temporal model for sexual risk behaviour with application to adolescent girls and young women in 13 sub-Saharan African countries

### 2022-01-19 src/docs_19-01-22-seth-sam/19-01-22-seth-sam.Rmd
Presentation for Seth / Sam's lab group

---
title: A multinomial spatio-temporal model for sexual risk behaviour with application to adolescent girls and young women in 13 sub-Saharan African countries
subtitle: HIV Inference Lab Group Meeting
author: Adam Howes
institute: Imperial College London
date: January 2022
bibliography: citations.bib
output:
  beamer_presentation:
    latex_engine: pdflatex
    highlight: haddock
    fig_width: 7 
    fig_height: 3
    includes:
        in_header: preamble.tex
---

@@

* Feedback on paper from people who know more about country contexts
* Connect more to policy. For example by replicating Katie's "number of new infections by risk group" spreadsheet
* Add logistic regression model for proportion of non-regular partner(s) who are KP

>>>>

---
title: A multinomial spatio-temporal model for sexual risk behaviour with application to adolescent girls and young women in 13 sub-Saharan African countries
subtitle: Statistics and Epidemiology Group Meeting
author: Adam Howes
institute: Imperial College London
date: January 2022
bibliography: citations.bib
output:
  beamer_presentation:
    latex_engine: pdflatex
    highlight: haddock
    fig_width: 7 
    fig_height: 3
    includes:
        in_header: preamble.tex
---

@@

* Have sent to Elona in Cape Town to get feedback
* Connecting more to policy, recently produced "new infections by risk group"
* Adding logistic regression model for proportion of non-regular partner(s) who are KP
